A Reduced Representation for Computational Fabrication

### 2013-05-03 thesis/1_cover_thesis.tex
add tex files

\Large \textbf{\textsf{ Spec2Fab: A Reducer-Tuner Model for Translating Specifications to 3D Prints
}} \\
\normalsize

@@

\vspace{.1in}
Donglai Wei \\

\vspace{.1in} B.S., Computer Science,
Carnegie Mellon University, 2011 \\

\vspace{.0in} S.M., Electrical Engineering and Computer Science,
M.I.T., 2013 \\

@@

Proposal for Thesis Research in Partial Fuillment\\
of the requirements for the degree of Master of Science\\

@@

>>>>

\Large \textbf{\textsf{ Your title goes here
}} \\
\normalsize

@@

\vspace{.1in}
Your name goes here \\

\vspace{.1in} B.S., Electrical Engineering,
some other school, 2010 \\

\vspace{.0in} S.M., Electrical Engineering and Computer Science,
M.I.T., 2012 \\

@@

Submitted to the Department of Electrical Engineering and Computer Science \\
in partial fulfillment of the requirements for the degree of \\

@@

Doctor of Philosophy \\ % <--- replace this with Master of Science if you want a master's instead
in Electrical Engineering and Computer Science \\
at the Massachusetts Institute of Technology \\
